### 2015-02-23 fundamentals/intro.tex
rm'd cafca example. it doesn't have great economic capability

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have
excellent capability in economics while capabailities for tracking transformations in
material isotopics and the effects of isotopics on technology performance are
neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
in this way, having elected to neglect isotopic resolution in favor of
integral effects.

>>>>

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others.
